---
params:
  new_bn: NA
  old_bn: NA
  hfserie_name: NA
  lfserie_name: NA
title: "Benchmark report `r params$hfserie_name` on `r params$lfserie_name`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: NULL
---

```{r include=F}
knitr::opts_chunk$set(fig.height = 2.5,dpi=49,out.width = "100%")
knitr::opts_knit$set(global.par = TRUE)
hfserie <- model.list(params$new_bn)$hfserie
hfserie <- hfserie[,colnames(hfserie) != "constant"]

presets_list <- presets_list_fun(hfserie,model.list(params$new_bn)$lfserie)
```

```{r include=FALSE}
graphpar <- par(mar = c(1,0,0,0))
```

# Presets

:::: {.columns}

::: {.column width="50%"}

**Before**

Model 1 (*differences --- with constant*)

```{r echo=FALSE}
autoplot(presets_list[[1]])
```

Model 3 (*levels --- with constant*)

```{r echo=FALSE}
autoplot(presets_list[[3]])
```

Model 5 (*levels --- without constant*)

```{r echo=FALSE}
autoplot(presets_list[[5]])
```

:::

::: {.column width="50%"}

**After**

Model 2 (*differences --- without constant*)

```{r echo=FALSE}
autoplot(presets_list[[2]])
```

Model 4 (*autocorrelated levels --- with constant*)

```{r echo=FALSE}
autoplot(presets_list[[4]])
```

Model 6 (*autocorrelated levels --- without constant*)

```{r echo=FALSE}
autoplot(presets_list[[6]])
```

:::

::::

# Benchmarks

:::: {.columns}

::: {.column width="50%"}

**Before**

```{r echo=FALSE,comment="\t"}
cat(disaggR:::benchmarkCall(params$new_bn,params$hfserie_name,params$lfserie_name))
```

:::


::: {.column width="50%"}

**After**

```{r echo=FALSE,comment="\t"}
cat(disaggR:::benchmarkCall(params$old_bn,params$hfserie_name,params$lfserie_name))
```

:::

::::

:::: {.columns}

::: {.column width="50%"}

```{r echo=FALSE}
autoplot(params$old_bn)
```

:::

::: {.column width="50%"}

```{r echo=FALSE}
autoplot(params$new_bn)
```

:::

::::

# In-sample predictions

:::: {.columns}

::: {.column width="50%"}

**Before**

```{r echo=FALSE}
autoplot(in_sample(params$old_bn,type="levels"))
autoplot(in_sample(params$old_bn,type="changes"))
```

:::

::: {.column width="50%"}

**After**

```{r echo=FALSE}
autoplot(in_sample(params$new_bn,type="levels"))
autoplot(in_sample(params$new_bn,type="changes"))
```

:::

::::

# Summary

:::: {.columns}

::: {.column width="50%"}

**Before**

```{r echo=FALSE}
print(summary(params$old_bn),call=FALSE)
```

:::

::: {.column width="50%"}

**After**

```{r echo=FALSE}
print(summary(params$new_bn),call=FALSE)
```

:::

::::

# Comparison with indicator

:::: {.columns}

::: {.column width="100%"}

```{r echo=FALSE,fig.width = 14}
autoplot(in_dicator(params$new_bn,type="levels-rebased"))
autoplot(in_dicator(params$new_bn,type="changes"))
autoplot(in_dicator(params$new_bn,type="contributions"))
```

:::

::::

# Revisions

:::: {.columns}

::: {.column width="100%"}

```{r echo=FALSE,fig.width=14}
autoplot(in_revisions(params$new_bn,params$old_bn,type="levels"))
autoplot(in_revisions(params$new_bn,params$old_bn,type="changes"))
autoplot(in_revisions(params$new_bn,params$old_bn,type="contributions"))
```

```{r include=F}
par(graphpar)
```

:::

::::